Gusto: a toolkit for compatible finite element dynamical cores

### 2025-02-06 source/paper.tex
fix FML intro

The finite element discretisation of each term in an equation is
represented in Firedrake by a UFL form object. FML defines a
\texttt{Label} object which is used to tag a UFL form to create a
\texttt{Term}, with the intention that the \texttt{Term} represents a
term in the residual.

FML defines a \texttt{Term} object that comprises the
\texttt{ufl.Form} defining the finite element discretisation of the
term and a dictionary of key-value pairs corresponding to the FML
\texttt{Label} objects that apply to this term. An FML \texttt{Label}
object has a name and an optional value, defaulting to \texttt{True}
to indicate the presence of the label. Labels can also be used to tag
parts of the form. For example, the \texttt{subject} label is used to
tag the \texttt{Function} in the \texttt{ufl.Form} that represents the
prognostic variable, or `subject' of the equation. These operations
are composable, so more than one label can be attached to a term. The
end result of labelling the terms in the residual is a
\texttt{LabelledForm} object that holds a list of terms, pairing
individual \texttt{ufl.Form} objects with FML labels. Labelled forms
can be added together, multiplied by floats and have additional terms
added. More complex manipulations are enabled by the
\texttt{label\_map} method that provides a way of filtering the terms
in the form based on their labels, applying different mappings to
terms that pass or fail the conditions defined in the filter. A common
operation might be to filter for terms that have a certain label, such
as \texttt{transport}, drop terms that do not have this label and
multiply those that do by the timestep. We shall demonstrate this in
the following example.

>>>>

The finite element discretisation of each term in an equation is
represented in Firedrake by a UFL form object. FML defines a
\texttt{Label} object which is used to tag a UFL form to create a
\texttt{Term}, with the intention that the \texttt{Term} represents a
term in the residual. The \texttt{Label} object consists of a name and
an optional value, defaulting to \texttt{True} to indicate the
presence of the label. Labels can be used to tag terms to identify
them as representing particular processes, such as transport, or they
can tag parts of the form. For example, the \texttt{subject} label is
used to tag the \texttt{Function} in the \texttt{ufl.Form} that
represents the prognostic variable, or `subject' of the
equation. These operations are composable, so more than one label can
be attached to a term. The end result of labelling the terms in the
residual is a \texttt{LabelledForm} object that holds a list of terms,
pairing individual \texttt{ufl.Form} objects with FML labels. Labelled
forms can be added together, multiplied by floating point numbers and
extended by adding additional terms. More complex manipulations are
enabled by the \texttt{label\_map} method that provides a way of
filtering the terms in the form based on their labels, applying
different mappings to terms that pass or fail the conditions defined
in the filter. A common operation might be to filter for terms that
have a certain label, such as \texttt{transport}, drop terms that do
not have this label and multiply those that do by the timestep. We
shall demonstrate this in the following example.
